R für die sozio-ökonomische Forschung

### 2020-09-24 Chap-Wahrscheinlichkeitstheorie.Rmd
comments c 1

ggplot2::ggplot(lambdas) +
  ggplot2::geom_point(aes(x=x, y=y, color=lambda, group=lambda)) +
  ggplot2::geom_line(aes(x=x, y=y, color=lambda, group=lambda)) + 
  ggplot2::scale_fill_discrete(name = "New Legend Title") +
  ggplot2::scale_y_continuous(expand = expansion(c(0,0), c(0,0.025))) +
  ggplot2::scale_x_continuous(expand = expansion(c(0,0), c(0,0))) +
  ggplot2::scale_color_icae(palette = "mixed", discrete = T) +
  ggplot2::ggtitle(TeX("Die Poisson-Verteilung für verschiedene $\\lambda$")) +
  ggplot2::guides(color = guide_legend(title = TeX("$\\lambda$"), 
                             title.position = "top")) + 
  theme_icae() + 
  ggplot2::theme(legend.title = element_text(), 
                       legend.position = "right")
```

@@

ggplot2::ggplot(lambda_4) +
  ggplot2::geom_point(aes(x=x, y=y, color=lambda, group=lambda)) +
  ggplot2::geom_line(aes(x=x, y=y, color=lambda, group=lambda)) + 
  ggplot2::scale_y_continuous(expand = expansion(c(0,0), c(0,0.025))) +
  ggplot2::scale_x_continuous(expand = expansion(c(0,0), c(0,0))) +
  ggplot2::scale_fill_discrete(name = "New Legend Title") +
  ggplot2::scale_color_icae(palette = "mixed", discrete = T) +
  ggplot2::ggtitle(TeX("Die Poisson-Verteilung für $\\lambda = 4$")) +
  ggplot2::geom_segment(aes(x = x_val, y = 0, 
                   xend = x_val, yend = y_val),
               colour = "#800080") +
  ggplot2::geom_segment(aes(x = 0, y = y_val, 
                   xend = x_val, yend = y_val),
               colour = "#800080") +
  ggplot2::geom_segment(aes(x = 3, y = y_val+0.05,
                   xend = 0, yend=y_val+0.0001),
               arrow = arrow(length = unit(0.03, "npc")),
               colour = "#800080") +
  ggplot2::annotate("text", 
           x = 3.8, y =y_val+0.0525, 
           label = "0.156",
           colour = "#800080") +
  ggplot2::guides(color = guide_legend(title = TeX("$\\lambda$"), 
                             title.position = "top")) + 
  theme_icae() + theme(legend.title = element_text(), 
                       legend.position = "none")
```

>>>>

ggplot2::ggplot(lambdas) +
  ggplot2::geom_point(aes(x=x, y=y, color=lambda, group=lambda)) +
  ggplot2::geom_line(aes(x=x, y=y, color=lambda, group=lambda)) + 
  ggplot2::scale_fill_discrete(name = "New Legend Title") +
  ggplot2::scale_y_continuous(expand = expansion(c(0,0), c(0,0.025))) +
  ggplot2::scale_x_continuous(expand = expansion(c(0,0), c(0,0))) +
  viridis::scale_color_viridis(discrete = T) +
  ggplot2::ggtitle(TeX("Die Poisson-Verteilung für verschiedene $\\lambda$")) +
  ggplot2::guides(color = guide_legend(title = TeX("$\\lambda$"), 
                             title.position = "top")) + 
  theme_icae() + 
  ggplot2::theme(legend.title = element_text(), 
                       legend.position = "right")
```

@@

ggplot2::ggplot(lambda_4) +
  ggplot2::geom_point(aes(x=x, y=y, color=lambda, group=lambda)) +
  ggplot2::geom_line(aes(x=x, y=y, color=lambda, group=lambda)) + 
  ggplot2::scale_y_continuous(expand = expansion(c(0,0), c(0,0.025))) +
  ggplot2::scale_x_continuous(expand = expansion(c(0,0), c(0,0))) +
  ggplot2::scale_fill_discrete(name = "New Legend Title") +
  viridis::scale_color_viridis(discrete = T) +
  ggplot2::ggtitle(TeX("Die Poisson-Verteilung für $\\lambda = 4$")) +
  ggplot2::geom_segment(aes(x = x_val, y = 0, 
                   xend = x_val, yend = y_val),
               colour = "#800080") +
  ggplot2::geom_segment(aes(x = 0, y = y_val, 
                   xend = x_val, yend = y_val),
               colour = "#800080") +
  ggplot2::geom_segment(aes(x = 3, y = y_val+0.05,
                   xend = 0, yend=y_val+0.0001),
               arrow = arrow(length = unit(0.03, "npc")),
               colour = "#800080") +
  ggplot2::annotate("text", 
           x = 3.8, y =y_val+0.0525, 
           label = "0.156",
           colour = "#800080") +
  ggplot2::guides(color = guide_legend(title = TeX("$\\lambda$"), 
                             title.position = "top")) + 
  theme_icae() + theme(legend.title = element_text(), 
                       legend.position = "none")
```
